### 2024-09-21 my_paper/manuscript_main.tex
add acs tables

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated, while parental education and self-reported Asian identity are positively associated. A one standard deviation increase in state-level bias is associated with a 4 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with 2 and 4 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory.

I report the results of the same regression but on sub-samples of second-generation immigrants by type of parents---interethnic and endogamous parents---in Figure (\ref{plot01-regression-byparent}). I present the results of estimating the main specification on second-generation immigrants in panel (A) and on sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that children of endogamous Asian marriages are more influenced by state-level bias than those of interethnic marriages. I find that a one standard deviation increase in state-level bias is associated with 5 percentage points decrease in self-reported Asian identity among children of AA parents.

I also report the results of the regression on sub-samples of third-generation immigrants by the number of Asian grandparents in Table (\ref{regtab-bygrandparents}). I find that state-level bias is not significantly associated with the self-reported Asian identity of children of interethnic grandparents. However, it is negatively associated with lower self-reported Asian identity of children of Asian grandparents. I find that a one standard deviation increase in state-level bias is associated with a 6 percentage points decrease in self-reported Asian identity.

@@

In this section, I explore the empirical relationship between state-level bias and interethnic marriages, as well as the migration patterns of second-generation Asian immigrants as robustness checks to my main analysis and the effect of proxy response on my results. I examine the impact of state-level biases on the likelihood of interethnic marriages, focusing on interethnic couples, and the migration decisions of Asian individuals within the United States.

I investigate the relationship between state-level bias and interethnic marriages. To this purpose, the regression specifications for the estimation will be as follows:

\begin{align}
Interethnic_{ist}^2 &= \beta_1^2 Bias_{st} + X_{ist}^2\pi + \gamma_{rt} 
            + \varepsilon_{ist}  \label{eq:inter-interethnic} 
\end{align}

Where $Interethnic_{ist}^2$ is an indicator variable that is equal to one if a couple is interethnic, i.e., a Asian husband-White wife or a White husband-Asian wife. $Bias_{st}$ is the average bias in state $s$ at time $t$, and $X_{ist}^2$ is a vector of partner-specific controls that would affect a marriage match that includes the wife's and husband's education, age, and years since immigrating to the United States.

I present the results of estimating equation (\ref{eq:inter-interethnic}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interethnic parents by 3 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in state-level bias is associated a 3 percentage points increase in the chances of a Asian husband marrying a White wife. A one standard deviation increase in state-level bias is associated a 4 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interethnic marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

@@

Additionally, state-level bias has a more substantial effect among second-generation immigrant children with Asian fathers and Asian mothers. A one standard deviation increase in bias correlates with a 5 percentage points decrease in self-reported Asian identity among second-generation Asian immigrant children of objectively Asian parents. I also find that bias positively correlates with interethnic marriage and not with migration decisions.

>>>>

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in state-level bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with a 8 percentage points decrease in self-reported Asian identity.

I report the results of the same regression but on sub-samples of second-generation immigrants by type of parents---interracial and endogamous parents---in Figure (\ref{plot01-regression-byparent}). I present the results of estimating the main specification on second-generation immigrants in panel (A) and on sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that children of interracial parents marriages are more influenced by state-level bias. I find that a one standard deviation increase in state-level bias is associated with a 5 percentage points decrease in self-reported Asian identity among children of endogamous parents---the estimate is statistically insignificant. However, a one standard deviation increase in state-level bias is associated with a 15 percentage points decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage points decrease in self-reported Asian identity among children of White fathers-Asian mothers.

I also report the results of the regression on sub-samples of third-generation immigrants by the number of Asian grandparents in Table (\ref{regtab-bygrandparents}). The overall effect of state-level bias on the different type of Asian children is negative, however, they are also mostly statistically insignificant. I find that a one standard deviation increase in state-level bias is associated with a 69 percentage points decrease in self-reported Asian identity among Asian children that have three grandparents that are born in an Asian country.

@@

In this section, I explore the empirical relationship between state-level bias and interracial marriages, as well as the migration patterns of second-generation Asian immigrants as robustness checks to my main analysis and the effect of proxy response on my results. I examine the impact of state-level biases on the likelihood of interracial marriages, focusing on interracial couples, and the migration decisions of Asian individuals within the United States.

I investigate the relationship between state-level bias and interracial marriages. To this purpose, the regression specifications for the estimation will be as follows:

\begin{align}
interracial_{ist}^2 &= \beta_1^2 Bias_{st} + X_{ist}^2\pi + \gamma_{rt} 
            + \varepsilon_{ist}  \label{eq:inter-interracial} 
\end{align}

Where $interracial_{ist}^2$ is an indicator variable that is equal to one if a couple is interracial, i.e., a Asian husband-White wife or a White husband-Asian wife. $Bias_{st}$ is the average bias in state $s$ at time $t$, and $X_{ist}^2$ is a vector of partner-specific controls that would affect a marriage match that includes the wife's and husband's education, age, and years since immigrating to the United States.

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 3 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in state-level bias is associated a 3 percentage points increase in the chances of a Asian husband marrying a White wife. A one standard deviation increase in state-level bias is associated a 4 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

@@

Additionally, state-level bias has a more substantial effect among second-generation immigrant children with Asian fathers and Asian mothers. A one standard deviation increase in bias correlates with a 5 percentage points decrease in self-reported Asian identity among second-generation Asian immigrant children of objectively Asian parents. I also find that bias positively correlates with interracial marriage and not with migration decisions.

### 2024-09-21 output/tables/tab46-iat-migration-tab.tex
add acs tables

\begin{table}[H]

\caption{Relationship Between Bias and Migration \label{regtab-mig-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
  & \specialcell{(1) \\ Migrated from \\ Birth Place} & \specialcell{(2) \\ Migrated from \\ Birth Place} & \specialcell{(3) \\ $Bias_{ist} - Bias_{ilb}$}\\
\midrule
$Bias_{st}$ & 1.05*** &  & \\
 & (0.18) &  & \\
$Bias_{lb}$ &  & 0.15 & \\
 &  & (0.59) & \\
Asian &  &  & 0.01**\\
 &  &  & (0.01)\\
Female & 0.00** & -0.01*** & 0.00\\
 & (0.00) & (0.00) & (0.00)\\
College Graduate: Mother & 0.01*** & 0.00 & -0.01**\\
 & (0.00) & (0.01) & (0.00)\\
College Graduate: Father & -0.03*** & -0.03*** & 0.01**\\
 & (0.01) & (0.01) & (0.00)\\
\midrule
Observations & 169,206 & 86,686 & 10,410\\
Mean & 0.15 & 0.15 & -0.06\\
Year $\times$ Region FE & X &  & \\
Birthyear $\times$ Birth Region FE &  & X & \\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equations (\ref{eq:migration-3}) in column (1), 
                      (\ref{eq:migration-4}) in column (2), and
                      (\ref{eq:migration-5}) in column (3).}
\item[2] \footnotesize{Column (1) is a regression where the left hand side variable is 
                      a dummy variable that is equal to one if a person migrated from the state
                      were born in and the right hand side variable is bias the year of survey.
                      Column (2) is a regression where the left hand side variable is 
                      a dummy variable that is equal to one if a person migrated from the state
                      were born in and the right hand side variable is bias the year of birth in the state of birth.
                      Column (3) is a regression where the left hand side variable is 
                      the difference between state-level bias during the year of the survey in the current state the 
                      respondent is living in, and state-level bias during the year of birth in the state of birth 
                      and the right hand side variable is self-reported Asian identity. This regression captures
                      the selection of those that self-reported Asian identity into states with different levels of bias.
                      I include controls for sex, quartic age, parental education, fraction of Asians in a state, and region × year fixed effects.
                      Standard errors are clustered on the state level.}
\item[3] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      Native-born second-generation Asian immigrant children with both
                      parents born in a Asian country. The sample in the column (3) regression is further restricted to only those that migrated from their birth state.}
\item[4] \footnotesize{Data source is the 2004-2021 Census Data.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Migration \label{regtab-mig-01}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
  & \specialcell{(1) \\ Migrated from \\ Birth Place} & \specialcell{(2) \\ Migrated from \\ Birth Place} & \specialcell{(3) \\ $Bias_{ist} - Bias_{ilb}$}\\
\midrule
$Bias_{st}$ & 0.13* &  & \\
 & (0.07) &  & \\
$Bias_{lb}$ &  & -0.03 & \\
 &  & (0.17) & \\
Asian &  &  & 0.02\\
 &  &  & (0.04)\\
Female & 0.00 & -0.01 & 0.00\\
 & (0.00) & (0.00) & (0.02)\\
College Graduate: Mother & 0.01*** & 0.00 & -0.01\\
 & (0.00) & (0.01) & (0.03)\\
College Graduate: Father & -0.03*** & -0.03*** & 0.03\\
 & (0.01) & (0.01) & (0.02)\\
\midrule
Observations & 73,563 & 41,641 & 2,075\\
Mean & 0.15 & 0.15 & -0.1\\
Year $\times$ Region FE & X &  & \\
Birthyear $\times$ Birth Region FE &  & X & \\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of equations (\ref{eq:migration-3}) in column (1), 
                      (\ref{eq:migration-4}) in column (2), and
                      (\ref{eq:migration-5}) in column (3).}
\item[2] \footnotesize{Column (1) is a regression where the left hand side variable is 
                      a dummy variable that is equal to one if a person migrated from the state
                      were born in and the right hand side variable is bias the year of survey.
                      Column (2) is a regression where the left hand side variable is 
                      a dummy variable that is equal to one if a person migrated from the state
                      were born in and the right hand side variable is bias the year of birth in the state of birth.
                      Column (3) is a regression where the left hand side variable is 
                      the difference between state-level bias during the year of the survey in the current state the 
                      respondent is living in, and state-level bias during the year of birth in the state of birth 
                      and the right hand side variable is self-reported Asian identity. This regression captures
                      the selection of those that self-reported Asian identity into states with different levels of bias.
                      I include controls for sex, quartic age, parental education, fraction of Asians in a state, and region × year fixed effects.
                      Standard errors are clustered on the state level.}
\item[3] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      Native-born second-generation Asian immigrant children with both
                      parents born in a Asian country. The sample in the column (3) regression is further restricted to only those that migrated from their birth state.}
\item[4] \footnotesize{Data source is the 2004-2021 Census Data.}
\end{tablenotes}
\end{threeparttable}}
\end{table}
